Algebraic Principles for Concurrency Verification Tools

### 2013-10-04 Paper/paper.tex
Updates to paper abstract

\author{Alasdair Armstrong \and Victor B.~F.~Gomes \and Georg Struth}

@@

\begin{abstract}
We investigate the laws required for the derivation of the
rely/guarantee and owicki-gries inference rules in a minimalistic
algebraic setting based on Kleene algebra...
\end{abstract}

@@

related work?

>>>>

\author{Alasdair Armstrong \and Victor B.~F.~Gomes\thanks{Sponsored by CNPq, Brazil} \and Georg Struth}

@@

We investigate equational laws for the derivation of rely-guarantee
style, Owicki-Gries style and separation logic style inference and
refinement rules in the minimalistic setting of semirings. The
algebraic level is linked with concrete programming models based on
languages and execution traces. The approach has been implemented in
Isabelle/HOL where the link between algebras and models supports
reasoning about both the control and data flow of concurrent
programs. This is illustrated by simple program verification examples.

@@
